% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[czech]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} 
\usepackage[czech]{babel}
\usepackage[sc,osf]{mathpazo}
\usepackage{multirow}
\usepackage{tabularx,colortbl}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{caption}
\usepackage{multicol}


%\setlength\voffset{-3.33in}
%\setlength\hoffset{-.25in}

%\setlength{\textheight}{23cm}
%\setlength{\oddsidemargin}{-6mm}
%\setlength{\textwidth}{7in} 

%\setlength{\hoffset}{-1.5cm} 
\setlength{\voffset}{-0.8cm}
%\footskip = 50pt
%\topskip = 20pt
%\setlength{\textheight}{20.0cm}
%\special{papersize=210mm,297mm} 
%\setlength{\textwidth}{26cm}

\captionsetup{tablename=}


%\definecolor{orange}{HTML}{A57164}
\definecolor{coolblack}{HTML}{002E63}
\definecolor{coffee}{HTML}{36454F}
% Set your name here
\def\name{Ing. Martin Kožený}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.5in},
  left=0.87in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.1in}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (+420) 724 735 822 \\
    Email: & \href{mailto:martin.kozeny@gmail.com}{\tt martin.kozeny@gmail.com}
    
    %LinkedIn: &
    %\url{http://cz.linkedin.com/pub/martin-kožený/41/601/556}
  \end{tabular}
\end{minipage}

\textcolor{coolblack}{\section*{Personal}}

\begin{itemize}
\item Born on December 21, 1986.
\item Czech Republic Citizen.
\item Marital status: single.
\item Driving licence: yes (B).
\item Spoken languages: Czech - mothertongue, English - fluent, German - good,
French - basic.
\end{itemize}

\textcolor{coolblack}{\section*{Profile}}
I have quite a lot experiences with programming in Java (both J2SE and server programming in J2EE) and recently started developing in JavaScript. I am also interested in other programming languages and using alternative
programming techniques. I passed during my studies many courses related to
artifical intelligence which is also object of my interest. In my current work I
deal with J2EE technologies, databases and client side development.

\textcolor{coolblack}{\section*{Education}}

\begin{itemize}
  \item Java SE 7 Programmer I Certification, February 2014
  \item Stanford University, Automata, January 2014
  \item École Polytechnique Fédérale de Lausanne, Principles of Reactive Programming, January 2014
  \item École Polytechnique Fédérale de Lausanne, Functional Programming Principles in Scala, December 2013
  \item Stanford University, Introduction to Mathematical Thinking, November 2013
  \item École Polytechnique Fédérale de Lausanne, Linear and Discrete Optimization, May 2013
  \item Stanford University Compilers online course, July 2012.
  \item Stanford University Game Theory online course, May 2012.
	\item Ing. Computer science - software engineering, Czech Technical University
  in Prague, 2009--2012.

  \item International exchange student of computer science, University of New
  Orleans, 2011.
  \item CISCO Networks certificate, CCNAE 1, 2010.
  
  \item Bc. Computer science, Czech Technical University in Prague, 2006--2009.
  \item First Certificate in English (FCE), 2006.
  \item Physics Olympiad -- regional round: 2nd place 2004, 4th place 2006;
  national round 2006 -- honorable mention.
  \item Grammar school Dašická Pardubice, graduated with honor, 1998--2006.
\end{itemize}


\textcolor{coolblack}{\section*{Employment}}

\begin{itemize}
\item Software developer at Oracle. December 2012--present.\\
\textit{Duties}: Developing desktop applications based on NetBeans Platform, working on NetBeans IDE itself primarily on apisupport ant project type. Working on Application Builder Cloud Service (ABCS), which is tool for Oracle Cloud. This includes client side (JavaScript, KnockoutJS, Jasmine, Atmosphere) and server side (Java, Maven, JUnit, JGroups) development.
\item Software developer at Arbes Technologies, s.r.o. May 2012--November 2012.\\
\textit{Duties}: Developing enterprise applications in Spring framework. Created own generic framework for CRUD operations.
\item Software developer at Ample cz s.r.o. November 2007--April 2012.\\
\textit{Duties}: Working on enterprise applications for government and for
private sector involving its designing, modeling and implementation. Experiences
with databases including data gathering and data normalizing for datawarehouse.
\item Tourist guide at Kinský dal Borgo, a.s. 2004--2011.\\
\textit{Duties}: Tourist guide at castle Kost in summer season.
\end{itemize}


\textcolor{coolblack}{\section*{Areas of expertise}}
\begin{multicols}{2} 
\textcolor{coffee}{\subsection*{Programming languages}}

\begin{itemize}
\item Java (J2SE, J2EE)
\item Scala
\item C/C++
\item Smalltalk
\item Ruby
\item Lisp
\item Prolog
\item Haskell
\end{itemize}


\textcolor{coffee}{\subsection*{Databases}}

\begin{itemize}
\item SQL language
\item MS SQL Server
\item MS SQL Server Analysis
\item Mondrian
\item PostgreSQL Server
\item Oracle and also its PL/SQL extension
\item MySQL
\end{itemize}
\end{multicols}




\textcolor{coffee}{\subsection*{Administration}}
\begin{itemize}
  \item Administration of Gnu/Linux
  
  \item MS Windows
  \item Mac OS
  
  \item Application server Tomcat
  \item JBoss
  \item Apache
  \item WebLogic 
  \item 
 % \item 
 % \item 
\end{itemize}
%\end{multicols}
%\newpage


\begin{multicols}{2} 
{\textcolor{coffee}{\subsection*{Web Development}}
\begin{multicols}{2}
\begin{itemize}
\item JBoss Seam
\item Spring
\item Ajax
\item CSS
\item HTML 5
\item XHTML
\item XML
\item Hibernate
\item UML 2.0
\item Web Services
\item JUnit testing
\item Javascript
\item Jasmine
\item SinonJS
\item Knockout
\item Oracle JET
\item JQuery
\item Atmosphere
\item JGroups
\item Jakarta Struts
\item PHP
\end{itemize}
\end{multicols}
}


\textcolor{coffee}{\subsection*{Tools}}

\begin{itemize}
\item Eclipse
\item NetBeans
\item Ant
\item Maven
\item Karma
\item Grunt
\item ETL graphs
\item Visual Studio
\item Enterprise Architect, Astah
\item CVS, SVN, Git
\end{itemize}
\end{multicols}


\textcolor{coffee}{\subsection*{Other}}
\begin{itemize}
\item Squander framework
\item \LaTeX
\item DocBook
 
\end{itemize}





\end{document}